### 2021-02-25 architecture.tex
Remove unused diagram node position specification
Improve architecture diagram

{ rank = same;
Problem [label="Problem P"];
pi [label=<Precedence &pi;> pos="10,10!"];
rho [label=<Precedence &rho;>];
}

Graphifier [style=rounded, label="Graph constructor"];
g [label="Graph"];
GCN [style=<rounded,bold>, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=<rounded,bold>, label="Output unit"];

{ rank = same;
SymbolCost [label="Symbol costs"];
LossFunction [style=rounded, label="Loss function"];
}

Sort [style=rounded, label="Sort"];

@@

Problem -> Graphifier -> g -> GCN;
GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [style=bold];
SymbolCost -> Sort -> Precedence;

>>>>

{ rank = same;
Problem [label="Problem P"];
pi [label=<Precedence &pi;>];
rho [label=<Precedence &rho;>];
}

Graphifier [style=rounded, label="Graph constructor"];
g [label="Graph"];
GCN [style=<rounded,bold>, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=<rounded,bold>, label="Output layer"];
SymbolCost [label="Symbol costs"];

{ rank = same;
Sort [style=rounded, label="Sort"];
LossFunction [style=rounded, label="Loss function"];
}

@@

Problem -> Graphifier -> g -> GCN;
GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [style=bold];
SymbolCost -> Sort;
Sort -> Precedence;
